A More Complete Algebra for File Synchronization

### 2015-11-19 2015/paper.tex
Minor improvements

\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}}

\newcommand{\descendant}{\prec}
\newcommand{\ancestor}{\succ}

\newcommand{\eqext}{\sqsubseteq}
\newcommand{\eqnrw}{\sqsupseteq}
\newcommand{\nequiv}{\not\equiv}
\newcommand{\indep}{\not\sim}

@@

% TODO: delete:
\newcommand{\np}{p_{\centernot\leftrightarrow}} % path not related to p TODO change this
\newcommand{\wrext}{\stackrel{\mathtt{br}}{\sqsubseteq}}
\newcommand{\wrnrw}{\stackrel{\mathtt{br}}{\sqsupseteq}}
\newcommand{\coworks}{\circ}
\newcommand{\ncoworks}{\centernot\circ}

\newcommand{\emptyseq}{[\,]}

\newcommand{\extset}[1]{\wp({#1})}
\newcommand{\orderset}[1]{\vec{\wp}({#1})}
\newcommand{\ordered}[1]{\vec{\mathbf{o}}({#1})}

\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
\newcommand{\reca}{\recchar{A}{B}{}} % Reconciliation
\newcommand{\recb}{\recchar{B}{A}{}}
\newcommand{\recaset}{\recchar{A}{B}{*}}
\newcommand{\recbset}{\recchar{B}{A}{*}}

@@

\newtheorem{myax}{Axiom}
\crefname{myax}{axiom}{axioms}

\newtheorem{mylem}{Lemma}
\crefname{mylem}{lemma}{lemmas}

@@

\newtheorem{myrul}{Rule}
\crefname{myrul}{rule}{rules}

@@

\begin{mydef}
Using $\FS[V/p]$ we denote a filesystem derived from $\FS$:
\[ \FS\{p\mapsto V\}(q) :=
   \begin{cases}
   V &\mbox{if~} q=p\\
   \FS(q) &\mbox{otherwise.}
   \end{cases}
\]
\end{mydef}

@@

\begin{mydef}{Minimal set / sequence.}
A sequence or set of commands is minimal if it contains at most one command on every path.
\end{mydef}

\begin{mydef}{Simple set / sequence.}
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

@@

% TODO A=B -> B=A; A=B B=C -> A=C; etc.

@@

\begin{myrul}
\[\infer{A\equiv B}{S;A;T\equiv S;B;T}\]
\end{myrul}

\begin{myrul}
\[\infer{A\eqext B}{S;A;T\eqext S;B;T}\]
\end{myrul}

@@

% \begin{myrul}
% \[\infer{\worksc{A_1,\ldots,A_i,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{A_i,A_1,\ldots,A_{i-1},A_{i+1},\ldots,A_n}{B_1,\ldots,B_n}}\]
% \end{myrul}

@@

% \begin{myrul}\label{r_w_replacecond}
% \[\inferr{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_n}}{\worksc{C}{B_n}}{\worksc{A_1,\ldots,A_n}{B_1,\ldots,B_{n-1},C}}\]
% \end{myrul}

@@

\begin{myrul}\label{r_invmove}
\[ \infer{\worksc{S;A}{B}}{\worksc{A}{S^{-1};B}} \]
To see the soundness of this rule...
Sequences are bijections on filesystems over type-equality.
TODO: $A,S,B$ need to be simple?
\end{myrul}

\begin{mydef}{Independent commands, sequences and sets.}
For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy;\czw\equiv\czw;\cxy\nequiv\cbrk$.
% TODO use w() instead of nequiv break
For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
\end{mydef}

\begin{myrul}\label{r_indep_combine}
\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T;U}{S}} \]
To see the soundness of this rule...
\end{myrul}

\begin{mylem}\label{indep_prefix_combine}
\[ \inferrr{\worksc{A;B}{S}}{\worksc{A;C}{S}}{B\indep C}{\worksc{A;B;C}{S}} \]
\end{mylem}
\begin{proof}
From \cref{r_invmove,r_indep_combine}
TODO reverse of /cref{r_invmove} needed
\end{proof}

@@

Pairs of commands in general will have the form
\[ \cxy(p,V_Y); \czw(q,V_W) \]
where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
and values are of the appropriate type: 
$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.

@@

\begin{myax}\label{ax_separate_commute}
Commands on unrelated paths commute:
$\cxy(p,V_Y); \czw(q,V_W) \equiv \czw(q,V_W); \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
TODO $p\neq q$
\end{myax}

\begin{myax}\label{ax_separate_nobreaks}
Commands on unrelated paths do not break every filesystem:
$\cxy(p,V_Y); \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
TODO $p\neq q$
\end{myax}

@@

\begin{myax}\label{ax_same_breaks}
Commands on the same path break every filesystem if incompatible:
$\cxy(p,V_Y); \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
\end{myax}

\begin{myax}\label{ax_same_emptyseq}
Commands on the same path simplify:
$\cxy(p,V_Y); \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
\end{myax}

\begin{myax}\label{ax_same_singlec}
Commands on the same path simplify:
$\cxy(p,V_Y); \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
\end{myax}

\begin{myax}\label{ax_distantchild_breaks}
$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
\end{myax}

\begin{myax}\label{ax_distantparent_breaks}
$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
TODO merge into previous
\end{myax}

\begin{mydef}{Construction pair.}
A pair of commands on paths $\pp$ and $p$ is a construction pair if $\pp=\parent(p)$ and the commands are one
of the following:
   \begin{gather*}
   % bd>bf
            [\cbd(\pp, D); \cbf(p, F)] \\
   % bd>bd
            [\cbd(\pp, D_1); \cbd(p, D_2)] \\
   % fd>bf
            [\cfd(\pp, D); \cbf(p, F)] \\
   % fd>bd
            [\cfd(\pp, D_1); \cbd(p, D_2)]
   \end{gather*}
\end{mydef}

\begin{mydef}{Destruction pair.}
A pair of commands on paths $p$ and $\pp$ is a destruction pair if $\parent(p)=\pp$ and the commands are one
of the following:
   \begin{gather*}
   % fb<db ??
            [\cfb(p); \cdb(\pp)] \\
   % fb<df ??
            [\cfb(p); \cdf(\pp, F)] \\
   % db<db ??
            [\cdb(p); \cdb(\pp)] \\
   % db<df ??
            [\cdb(p); \cdf(\pp, F)]
   \end{gather*}
\end{mydef}

\begin{myax}\label{ax_directchild_breaks}
$\cxy(\pp,V_Y); \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
\end{myax}

\begin{myax}\label{ax_directparent_breaks}
$\cxy(p,V_Y); \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
\end{myax}

\begin{myax}\label{ax_child_assert}
An assertion command can be added on a child path:
$\cbb(p);\cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y);\cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
\end{myax}

\begin{myax}\label{ax_parent_assert}
An assertion command can be added on the parent path:
$\cdd(\pp);\cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y);\cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
\end{myax}

@@

\begin{myax}\label{worksextpostfix}
$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences of commands
\end{myax}

@@

\begin{myth}
If $A, B$ are simple, then $\worksc{B;\reca}{A,B}$
\end{myth}

@@

We therefore have a minimal $B'$ which has a command on $q$ just before $\cxy(p, V_Y)$ and $B'\equiv B$.
Let this command on $q$ be $\cqr(q, V_R)$.
\begin{gather*}
A = \cdots; \czw(q, V_W); \cxy(p, V_Y); \cdots \\
B' = \cdots; \cqr(q, V_R); \cxy(p, V_Y); \cdots
\end{gather*}

@@

We would like to prove that $\worksc{B;\reca}{A,B}$.
From above we know that this is equivalent to
$\worksc{\ordered{A\cap B};\ordered{B\setminus A};\reca}{A,B}$.
As we already know that $\reca\indep B\setminus A$
and that $\worksc{\ordered{A\cap B};\ordered{B\setminus A}}{A,B}$
(as $\worksc{B}{A,B}$),
based on \cref{indep_prefix_combine}
we only need to prove that
$\worksc{\ordered{A\cap B};\reca}{A,B}$.

\newcommand{\acbi}{\ordered{A\cap B}^{-1}}
\newcommand{\amb}{A\setminus B}
\newcommand{\bma}{B\setminus A}
Using \cref{r_invmove} we can rephrase this as
% TODO axiom doesn't specify multiple conditions
$\worksc{\reca}{\acbi;A,\acbi;B}$.

We already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
% \item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksc{\ordered{\amb};\ordered{\bma}}{\acbi;A,\acbi;B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
\end{itemize}

@@

We also know that there must be a command $\cqr(r,V_R)$ in $T$ which is not independent of $\czw(q,V_W)$.
By definition this means that one of the following must be true:
\begin{itemize}
\item $\czw(q,V_W);\cqr(r,V_R) \equiv\cbrk$
\item $\cqr(r,V_R);\czw(q,V_W) \equiv\cbrk$
\item $\czw(q,V_W);\cqr(r,V_R) \nequiv \cqr(r,V_R);\czw(q,V_W)$
\end{itemize}
From these and \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
either $q\descendant r$ or $r\descendant q$.
By definition we also know that $\cxy(p,V_Y)\indep \cqr(r,V_R)$,
and the same argument shows that therefore
$p\not\descendant r$ and $r\not\descendant p$ and $p\neq r$. TODO CHECK

@@

We know that $T$ cannot have a command on $q$ as $q=\parent(p)$ and $\cxy(p,V_Y)\indep T$.
Create $T'\equiv T$ by inserting a command on $q$ before $\cqr(r,V_R)$
into $T$ according to \cref{ax_parent_assert}.
We now have $\cxy(p,V_Y)\indep T\equiv T'$ which is a contradiction as
$T'$ has a command on $q$ and $q=\parent(p)$.
% TODO axiom? A \~ B == C  =>  A \~ C
\end{proof}

>>>>

\newcommand{\typeset}{\{\fsregcommandchar{D},\fsregcommandchar{F},\empt\}} % Set of types in commands
\newcommand{\cc}{\circ}
\newcommand{\descendant}{\prec}
\newcommand{\ancestor}{\succ}

\newcommand{\eqext}{\sqsubseteq}
\newcommand{\eqnrw}{\sqsupseteq}
\newcommand{\nequiv}{\not\equiv}
\newcommand{\indep}{\wr\!\!\wr\,} % Independent

@@

\newcommand{\emptyseq}{[\,]} % TODO change

\newcommand{\extset}[1]{\wp({#1})}
\newcommand{\orderset}[1]{\vec{\wp}({#1})}
\newcommand{\ordered}[1]{#1}

\newcommand{\recchar}[3]{{#1}^{#3}_{\mathcal{R}|{#2}}}
\newcommand{\reca}{\recchar{A}{B}{}} % Reconciled from A
\newcommand{\recb}{\recchar{B}{A}{}}
\newcommand{\recaset}{\recchar{A}{B}{*}}
\newcommand{\recbset}{\recchar{B}{A}{*}}

@@

\newtheorem{myax}{Axiom}
\crefname{myax}{axiom}{axioms}
% \creflabelformat{myax}{A#2#1#3}

\newtheorem{mylem}{Lemma}
\crefname{mylem}{lemma}{lemmas}
% \creflabelformat{mylem}{L#2#1#3}

@@

\newtheorem{myrul}{Rule}
\crefname{myrul}{rule}{rules}
% \creflabelformat{myrul}{R#2#1#3}

@@

\begin{mydef}
Using $\FS[V/p]$ we denote a filesystem derived from $\FS$:
\[ \FS[V/p](q) :=
   \begin{cases}
   V &\mbox{if~} q=p\\
   \FS(q) &\mbox{otherwise.}
   \end{cases}
\]
\end{mydef}

@@

\begin{mydef}{Minimal set or sequence.}
A sequence or set of commands is minimal if it contains at most one command on every path.
\end{mydef}

\begin{mydef}{Simple set or sequence.}
A sequence or set of commands is simple if it is minimal and it does not contain assertion commands.
\end{mydef}

@@

@@

\begin{myrul}
\[\infer{A\equiv B}{S\cc A\cc T\equiv S\cc B\cc T}\]
\end{myrul}

\begin{myrul}
\[\infer{A\eqext B}{S\cc A\cc T\eqext S\cc B\cc T}\]
\end{myrul}

@@

@@

@@

\begin{myrul}\label{r_invmove}
\[ \infer{\worksc{S\cc A}{B}}{\worksc{A}{S^{-1}\cc B}} \]
To see the soundness of this rule...
Sequences are bijections on filesystems over type-equality.
TODO: $A,S,B$ need to be simple?
\end{myrul}

\begin{mydef}{Independent commands, sequences and sets.}
For two commands $\cxy$ and $\czw$ we write $\cxy\indep\czw$ if $\cxy\cc \czw\equiv\czw\cc \cxy\nequiv\cbrk$.
% TODO use w() instead of nequiv break
For two sequences or sets of commands $A$ and $B$ we write $A\indep B$ if
$\forall a\in A \mbox{and~} \forall b\in B: a\indep b$.
\end{mydef}

\begin{myrul}\label{r_indep_combine}
\[ \inferrr{\worksc{T}{S}}{\worksc{U}{S}}{T\indep U}{\worksc{T\cc U}{S}} \]
To see the soundness of this rule...
\end{myrul}

\begin{mylem}\label{indep_prefix_combine}
\[ \inferrr{\worksc{A\cc B}{S}}{\worksc{A\cc C}{S}}{B\indep C}{\worksc{A\cc B\cc C}{S}} \]
\end{mylem}
\begin{proof}
From \cref{r_invmove,r_indep_combine}
TODO reverse of \cref{r_invmove} needed
\end{proof}

@@

Pairs of commands in general will have the form
\[ \cxy(p,V_Y)\cc  \czw(q,V_W) \]
where $X,Y,Z,W\in\typeset$, $p,q\in\setp$, 
and values are of the appropriate type: 
$V_Y\in\setvx{Y}$ and $V_W\in\setvx{W}$.

@@

\begin{myax}\label{ax_separate_commute}
Commands on unrelated paths commute:
$\cxy(p,V_Y)\cc  \czw(q,V_W) \equiv \czw(q,V_W)\cc  \cxy(p,V_Y)$ where $p\not\descendant q$ and $q\not\descendant p$.
TODO $p\neq q$
\end{myax}

\begin{myax}\label{ax_separate_nobreaks}
Commands on unrelated paths do not break every filesystem:
$\cxy(p,V_Y)\cc  \czw(q,V_W) \nequiv \cbrk$ where $p\not\descendant q$ and $q\not\descendant p$.
TODO $p\neq q$
\end{myax}

@@

\begin{myax}\label{ax_same_breaks}
Commands on the same path break every filesystem if incompatible:
$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $Y\ne Z$.
\end{myax}

\begin{myax}\label{ax_same_emptyseq}
Commands on the same path simplify:
$\cxy(p,V_Y)\cc  \czw(p,V_W) \eqext \emptyseq$ where $Y=Z$ and $X=W=\fsregcommandchar{\empt}$ or $X=W=\fsregcommandchar{D}$.
\end{myax}

\begin{myax}\label{ax_same_singlec}
Commands on the same path simplify:
$\cxy(p,V_Y)\cc  \czw(p,V_W) \equiv \cxw(p,V_W)$ where $Y=Z$ and $XW\neq\cbb$ and $XW\neq\cdd$.
\end{myax}

\begin{myax}\label{ax_distantchild_breaks}
$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp\descendant p$ and $\pp\neq\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.
\end{myax}

\begin{myax}\label{ax_distantparent_breaks}
$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $p\ancestor \pp$ and $\parent(p)\neq \pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.
TODO merge into previous
\end{myax}

\begin{mydef}{Construction pair.}
A pair of commands on paths $\pp$ and $p$ is a construction pair if $\pp=\parent(p)$ and the commands are one
of the following:
   \begin{gather*}
   % bd>bf
            [\cbd(\pp, D)\cc  \cbf(p, F)] \\
   % bd>bd
            [\cbd(\pp, D_1)\cc  \cbd(p, D_2)] \\
   % fd>bf
            [\cfd(\pp, D)\cc  \cbf(p, F)] \\
   % fd>bd
            [\cfd(\pp, D_1)\cc  \cbd(p, D_2)]
   \end{gather*}
\end{mydef}

\begin{mydef}{Destruction pair.}
A pair of commands on paths $p$ and $\pp$ is a destruction pair if $\parent(p)=\pp$ and the commands are one
of the following:
   \begin{gather*}
   % fb<db ??
            [\cfb(p)\cc  \cdb(\pp)] \\
   % fb<df ??
            [\cfb(p)\cc  \cdf(\pp, F)] \\
   % db<db ??
            [\cdb(p)\cc  \cdb(\pp)] \\
   % db<df ??
            [\cdb(p)\cc  \cdf(\pp, F)]
   \end{gather*}
\end{mydef}

\begin{myax}\label{ax_directchild_breaks}
$\cxy(\pp,V_Y)\cc  \czw(p,V_W) \equiv \cbrk$ where $\pp=\parent(p)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$
and the pair is not a construction pair.
\end{myax}

\begin{myax}\label{ax_directparent_breaks}
$\cxy(p,V_Y)\cc  \czw(\pp,V_W) \equiv \cbrk$ where $\parent(p)=\pp$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$
and the pair is not a destruction pair.
\end{myax}

\begin{myax}\label{ax_child_assert}
An assertion command can be added on a child path:
$\cbb(p)\cc \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y) \equiv \cxy(\pp,V_Y)\cc \cbb(p)$ where $\pp\descendant p$ and $\cxy\neq\cdd$.
\end{myax}

\begin{myax}\label{ax_parent_assert}
An assertion command can be added on the parent path:
$\cdd(\pp)\cc \cxy(p,V_Y) \equiv \cxy(p,V_Y) \equiv \cxy(p,V_Y)\cc \cdd(\pp)$ where $\pp\descendant p$ and $\cxy\neq\cbb$.
\end{myax}

@@

\begin{myax}\label{worksextpostfix}
$\worksc{A}{A\cc S}$ where $A$ and $S$ are arbitrary sequences of commands
\end{myax}

@@

\begin{myth}
If $A, B$ are simple, then $\worksc{B\cc \reca}{A,B}$
\end{myth}

@@

We therefore have a minimal $B'$ which has a command on $q$ just before $\cxy(p, V_Y)$ and $B'\equiv B$.
Let this command on $q$ be $\cqr(q, V_R)$.
\begin{gather*}
A = \cdots\cc  \czw(q, V_W)\cc  \cxy(p, V_Y)\cc  \cdots \\
B' = \cdots\cc  \cqr(q, V_R)\cc  \cxy(p, V_Y)\cc  \cdots
\end{gather*}

@@

We would like to prove that $\worksc{B\cc \reca}{A,B}$.
From above we know that this is equivalent to
$\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}\cc \reca}{A,B}$.
As we already know that $\reca\indep B\setminus A$
and that $\worksc{\ordered{A\cap B}\cc \ordered{B\setminus A}}{A,B}$
(as $\worksc{B}{A,B}$),
based on \cref{indep_prefix_combine}
we only need to prove that
$\worksc{\ordered{A\cap B}\cc \reca}{A,B}$.

\newcommand{\acbi}{\ordered{A\cap B}^{-1}}
\newcommand{\amb}{A\setminus B}
\newcommand{\bma}{B\setminus A}
Using \cref{r_invmove} we can rephrase this as
% TODO axiom doesn't specify multiple conditions
$\worksc{\reca}{\acbi\cc A,\acbi\cc B}$.

We already know the following things:
\begin{itemize}
\item $\amb$ and $\bma$ are simple as $A$ and $B$ are simple
% \item $\amb \cap \bma = \emptyset$
\item $\reca$ is the largest subset of $\amb$ for which $\reca\indep\amb$
\item $\worksc{\ordered{\amb}\cc \ordered{\bma}}{\acbi\cc A,\acbi\cc B}$ as $\worksc{A,B}{A,B}$ based on \cref{r_invmove}
\end{itemize}

@@

We also know that there must be a command $\cqr(r,V_R)$ in $T$ which is not independent of $\czw(q,V_W)$.
By definition this means that one of the following must be true:
\begin{itemize}
\item $\czw(q,V_W)\cc \cqr(r,V_R) \equiv\cbrk$
\item $\cqr(r,V_R)\cc \czw(q,V_W) \equiv\cbrk$
\item $\czw(q,V_W)\cc \cqr(r,V_R) \nequiv \cqr(r,V_R)\cc \czw(q,V_W)$
\end{itemize}
From these and \cref{ax_separate_commute,ax_separate_nobreaks} we also know that
either $q\descendant r$ or $r\descendant q$.
By definition we also know that $\cxy(p,V_Y)\indep \cqr(r,V_R)$,
and the same argument shows that therefore
$p\not\descendant r$ and $r\not\descendant p$ and $p\neq r$. TODO CHECK

@@

We know that $T$ cannot have a command on $q$ as $q=\parent(p)$ and $\cxy(p,V_Y)\indep T$.
Create $T'\equiv T$ by inserting a command on $q$ before $\cqr(r,V_R)$
into $T$ according to \cref{ax_parent_assert}.
We now have $\cxy(p,V_Y)\indep T\equiv T'$ which is a contradiction as
$T'$ has a command on $q$ and $q=\parent(p)$.

\end{proof}
